---
output:
  github_document:
  html_preview: false
bibliography: inst/references.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pricediscovery: Price discovery analysis under "one-security-many-markets" setting

<!-- badges: start -->
<!-- badges: end -->


The `pricediscovery` pacakge is used to conduct price discovery analysis according to the @Hasbrouck1995's "one-security-many-markets" setting. Current version can calculate @Gonzalo1995's component shares (CSs), @Hasbrouck1995's information shares (ISs), and @Putnins2013's information leadership shares.

This package tries to implement such an empirical setting in an easy way. I would particularly focus on a case where the number of markets N > 2 as prior implementation is restrictive to bi-variable setting.

This package also helps to resample the price series. Raw financial data might be in tick level, or the data frequency between markets is not the same. Hence, a resampling is needed when conducting price discovery analysis.

## Background
Financial price discovery characterizes how information is incorporated into the fundamental values and many studies have suggested this process across multiple venues. The price discovery happens when the same security is traded among different venues, such as E-mini S&P 500 futures and SPY, the ETF. Knowing which market is informative to price formation process is important for market participants, especially for regulators, to understand the dynamics of market microstructure. This is also helpful for intraday arbitragers to understand better for lead-lag relationship. 

## Methodology
For full methodological details, see the package vignette:

```r
vignette("methodology", package = "pricediscovery")
```

## Installation

You can install the development version of pricediscovery like so:

```r
#install.packages("devtools")
devtools::install_github("richie-ma/pricediscovery")
library(pricediscovery)
```

## Example
I use a sample dataset for BTC-USD trade prices from five major cryptocurrecny exchanges: Kraken, Gemini, Coinbase, Bitstamp, and Bitfinex on January 5, 2026. 

### Data resampling
Let's resample every market data to 1-second frequency and then merge all together.

``` {r, cache=TRUE}

### using the test datasets
library(ggplot2)
library(pricediscovery)
kraken <- readRDS(testthat::test_path("btcusd_kraken.rds"))[, .(time, kraken=price)]
gemini <- readRDS(testthat::test_path("btcusd_gemini.rds"))[, .(time, gemini=price)]
coinbase <- readRDS(testthat::test_path("btcusd_coinbase.rds"))[, .(time, coinbase=price)]
bitstamp <- readRDS(testthat::test_path("btcusd_bitstamp.rds"))[, .(time, bitstamp=price)]
bitfinex <- readRDS(testthat::test_path("btcusd_bitfinex.rds"))[, .(time, bitfinex=price)]

mkt_data <- list(kraken = resample(kraken, 'time', 'secs', 1, "00:00:00", "23:59:59"), 
                 gemini = resample(gemini, 'time', 'secs', 1, "00:00:00", "23:59:59"), 
                 coinbase = resample(coinbase, 'time', 'secs', 1, "00:00:00", "23:59:59"), 
                 bitstamp = resample(bitstamp, 'time', 'secs', 1, "00:00:00", "23:59:59"), 
                 bitfinex = resample(bitfinex, 'time', 'secs', 1, "00:00:00", "23:59:59"))

mkt_data_1s <- Reduce(
  function(x, y) merge(x, y, by = "DT"),
  mkt_data
)

mkt_data_1s

ggplot(data = mkt_data_1s, aes( x = DT))+
  geom_line(aes(y = KRAKEN, color='KRAKEN'))+
  geom_line(aes(y = GEMINI, color='GEMINI'))+
  geom_line(aes(y = COINBASE, color='COINBASE'))+
  geom_line(aes(y = BITSTAMP, color='BITSTAMP'))+
  geom_line(aes(y = BITFINEX, color='BITFINEX'))+
  labs(
    x = "Time",
    y = "Price",
    color = "Market"
  )
```

One can see that prices in the five markets are close to each other and move together, suggesting that there should not be persistent deviations between one another.

### Price discovery analyses
Now, I calculate the price discovery shares. I select the lag based on SC with maximum lag 60, corresponding to 1 minute. In long-run equilibrium, I add a constant term to account for the price level differences between them. I use the standard cointgrating beta which is set to

$$
\begin{bmatrix}
1 & -1 & 0 & 0& 0\\
1 & 0 & -1 & 0& 0\\
1 & 0 & 0 & -1& 0\\
1 & 0 & 0 & 0& -1\\
\end{bmatrix}
$$

```{r,  cache=TRUE}
price_discovery_measures <- price_discovery(mkt_data_1s, 
                                            num_market = 5,
                                            price_columns = c("KRAKEN", 
                                                              "GEMINI", 
                                                              "COINBASE", 
                                                              "BITSTAMP", 
                                                              "BITFINEX"),
                                            log_price = TRUE,
                                            lag_selection = TRUE,
                                            vecm_max.lag = 60, 
                                            lag_select_ceritera = 'SC',
                                            coin_const = TRUE,
                                            coin_beta = TRUE)
price_discovery_measures                                             
                                            
```
I find that 

- In terms of efficiency, measuring which market price is more informative about common efficient price:  Coinbase contributes the most to the common efficient price with information shares (ISs) reaching to 65.94%, followed by Bitfinex (25.54%) and Bitstamp (7.17%).

- In terms of timeliness, measuring which market incorporates the new information faster: Based on information leadership shares (ILSs), Bitstamp is the first one to incorporate new information into prices, followed by Gemini, and Kraken. 

- This exercise suggests that the timeliness and efficiency of price discovery might not occur in the same market. 

- CS typically shows a similar pattern as ILS.

## References



